Continuous gravitational waves in the lab: recovering audio signals with a table-top optical microphone

### 2021-05-05 paper/paper_main.tex
modifying abstract to mention supplementary material

\author{\textbf{[Authors removed for double-anonymous review.]}}

@@

\begin{abstract}
Gravitational-wave observatories around the world are searching for continuous waves: persistent signals from sources such as spinning neutron stars. 
These searches use sophisticated statistical techniques to look for weak signals in noisy data. 
In this paper, we demonstrate these techniques using a table-top model gravitational-wave detector: a Michelson interferometer where sound is used as an analog for gravitational waves. 
Using signal processing techniques from continuous-wave searches, we demonstrate the recovery of tones with constant and wandering frequencies. 
We also explore the use of the interferometer as a teaching tool for educators in physics and electrical engineering by using it as an ``optical microphone'' to capture music and speech. 
% \jam{We mention undergraduate labs twice, roll this sentence into the end? Also, electrical sounds weird, why the change from electrical engineering?}
%The interferometer is used as an ``optical microphone'' to capture music and speech. 
% \jam{I changed all the \emph to ``'', feel free to change them back, but I think it is more explicit this way}
We present a range of example filtering techniques to recover the original signal from noisy data, including a bandpass filter, notch filters, a Wiener filter, and the statistical log minimum mean-square-error (logMMSE) estimator.
% log minimum mean-square-error (logMMSE) estimator
Recordings of simple chords and drums are easily recovered, but complex music and speech are more challenging. 
This demonstration can be used by educators in undergraduate laboratories and can be adapted for use as an engagement tool for communicating gravitational-wave and signal-processing topics to non-specialist audiences. 
% This demonstration has scope for use by educators in undergraduate laboratories and can be adapted for use as an engagement tool for communicating gravitational-wave and signal-processing topics to non-specialist audiences. 
% rearranged in response to Anna's pnp review
%Finally we use the interferometer as an `optical microphone' to capture music and speech and apply filtering techniques to recover the original signals from the noisy data. Such techniques include simple bandpass filtering, notch filters, a Weiner filter, and the statistical logMMSE method.  
%Simple chords and drums are easily recovered, but complex music and speech are more challenging. 
%This demonstration has scope for use in physics and electrical engineering undergraduate laboratories. 
%It can also be adapted for use as an engagement tool for communicating gravitational wave and signal-processing topics to non-specialist audiences. 
\end{abstract}

>>>>

%\author{\textbf{[Authors removed for double-anonymous review.]}}

@@

\begin{abstract}
Gravitational-wave observatories around the world are searching for continuous waves: persistent signals from sources such as spinning neutron stars. 
These searches use sophisticated statistical techniques to look for weak signals in noisy data. 
In this paper, we demonstrate these techniques using a table-top model gravitational-wave detector: a Michelson interferometer where sound is used as an analog for gravitational waves. 
Using signal processing techniques from continuous-wave searches, we demonstrate the recovery of tones with constant and wandering frequencies. 
We also explore the use of the interferometer as a teaching tool for educators in physics and electrical engineering by using it as an ``optical microphone'' to capture music and speech. 
% \jam{We mention undergraduate labs twice, roll this sentence into the end? Also, electrical sounds weird, why the change from electrical engineering?}
%The interferometer is used as an ``optical microphone'' to capture music and speech. 
% \jam{I changed all the \emph to ``'', feel free to change them back, but I think it is more explicit this way}
In the accompanying Supplementary Material we consider a range of example filtering techniques to recover the original signal from noisy data and present highlight results here. 
%We present a range of example filtering techniques to recover the original signal from noisy data, including a bandpass filter, notch filters, a Wiener filter, and the statistical log minimum mean-square-error (logMMSE) estimator.
% log minimum mean-square-error (logMMSE) estimator
Recordings of simple chords and drums are easily recovered, but complex music and speech are more challenging. 
This demonstration can be used by educators in undergraduate laboratories and can be adapted for use as an engagement tool for communicating gravitational-wave and signal-processing topics to non-specialist audiences. 
% This demonstration has scope for use by educators in undergraduate laboratories and can be adapted for use as an engagement tool for communicating gravitational-wave and signal-processing topics to non-specialist audiences. 
% rearranged in response to Anna's pnp review
%Finally we use the interferometer as an `optical microphone' to capture music and speech and apply filtering techniques to recover the original signals from the noisy data. Such techniques include simple bandpass filtering, notch filters, a Weiner filter, and the statistical logMMSE method.  
%Simple chords and drums are easily recovered, but complex music and speech are more challenging. 
%This demonstration has scope for use in physics and electrical engineering undergraduate laboratories. 
%It can also be adapted for use as an engagement tool for communicating gravitational wave and signal-processing topics to non-specialist audiences. 
\end{abstract}
